---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# gorkagram

<!-- badges: start -->
<!-- badges: end -->

This R package draws gorkagrams.

A gorkagram is a graph depicting a value of a variable in
a qualitative semantic differential with labelled polarities. The
depiction of the value is not supposed to be exact, but instead,
in conjunction with its label, to be evocative of a degree of
proximity to a polarity. 

The original gorkagram appears as "Diagram Nine" in 

> Gorka, S. (2007) Content and end-state-based alteration in the practice of political violence since the end of cold war: the difference between the terrorism of the cold war and the terrorism of al Qaeda: the rise of the "transcendental terrorist". PhD Dissertation, Corvinus University, 166.

## Example

To draw a gorkagram, specify the polarities (`from`, `to`), a label
for the variable of interest (`what`), and it's placement (`what`) between polarities, from 0 to 1. 

```{r example}
library(gorkagram)
gorkagram(from = "Spread", 
          to = "Dip",
          what = "Hummus", 
          where = 35/100)
```

The seemingly misaligned graphical elements are indeed features of the original gorkagram, and not bugs. To adjust graphical elements, use the remaining arguments of function `gorkagram`.

## Installation

This is a toy package and you should absolutely not install it ever,
lest you bring upon us the demise of Western Civilization.

If your goal is, however, to bring such demise upon us, install with:

``` r
# install.packages("devtools")
devtools::install_github("diogomarques/gorkagram")
```

But please don't.
